Space Matters: extending sensitivity analysis to initial spatial conditions in geosimulation models

### 2018-09-28 Response_to_Reviewers.tex

Concerning specifically the comments made by the first referee:

\begin{itemize}
	% 1. I think it would be better if the author would focus on a single model. This way they could describe the model and the analyses in more detail. As it stands, the models are treated as black boxes. 
	\item The suggestion to focus on a single model is a qualified comment. However, after presenting our research to several audiences, we came to the conclusion that the genericity of our approach would be better served by two case studies rather than with a single model. In that perspective, the ``black-box'' is seen as an advantage as it reinforces genericity. We acknowledge the fact that this choice led us to shorten the model presentations. Nevertheless, we have taken notice of your remark by improving the description of the models and their results through the addition of pseudo-codes in Appendix, result descriptions in the text and by recalling more clearly the link to the model source we used. Furthermore, we have focused on some of the most classical models of the ABM literature so as to lower the reader's cost of entry into the methodology.

   % I believe it would be better to begin with an illustrative example on how two or three initial patterns influence the model results and then use the suggested method for a more extensive analysis
   \item We agree that illustrative examples would provide a relevant starting point to  the analysis but we were afraid that their addition to the paper would make the introduction less straightforward and have the opposite effect to the one we were seeking. As we were nevertheless very interested by your remark, we provide a short answer to your proposition.

In order to get a first idea of the potential impact of spatial initial conditions on to the results of the simulation, we implemented on the Schelling Segregation model a geographical constraint: some cells cannot be inhabited (yellow cells in Figure 1). The way those “forbidden” cells are distributed throughout space will indeed influence the steps of the model. 
We introduced various spatial initial conditions in the model that we controlled by one clustering parameter on the forbidden cells. A value of 0 would indicate a spatial distribution of yellow cells so as to minimize spatial autocorrelation. A value of 1 indicates on the contrary a concentration process that tends towards a high value of autocorrelation (see below Figure 1). % note : no fig envt in moderncv

@@

	% 4. Consider replacing “meta parameters” with something like “generator parameters” or “initial pattern parameters.”
	\item We agree that the term of meta-parameters may have been confusing, and following the suggestion we replaced it with ``generator parameters''.

	% 5. Line 228: Please explain why the median was chosen. Especially given that you use an L2 norm and variances in the index
    \item There was a mistake in the writing, as we never use the median but always the mean, which as you recall is consistent with the choice of distance we made. This was corrected in the paper.

	% 6. Line 232: comparing phase diagrams is related to the topic of comparing patterns. It would make sense to mention the methods that are usually used to compare patterns
	\item Some general references on comparing patterns were added.

	% 7. Line 238: Please explain why this particular index was chosen and discuss its properties. Connect the discussion to other indices like L1, and Linf norms, etc. Would we get qualitatively different results from different indices? 
	\item The approach proposed in the paper is indeed rather exploratory. This explains why we have chosen to focus on a single index (L2) as this index is relatively well-known in the community. Previous exploratory analyses have shown that the results were rather stable when using the Monge method. Adapting the mathematical aggregator to the different indices would constitute an interesting perspective, but is out of the scope of the paper which already focuses on two models and proposes a new framework for analysing the impact of initial pattern parameters. We however added a supplementary material showing the distances obtained with other distances, which are similar to the results in main text.

@@

	% 8. Regarding the spatial generator: the authors should explain why this generator is relevant to these two models? 
	\item This spatial generator is relevant to both model as it produces density grids at a ``metropolitan scale'' (see detailed discussion added in Appendix and the original paper from which we used the generator), which is the scale at which both model were initially intended to be. We made this aspect more explicit.

	\item More particularly concerning the choice of this generator in the case of Schelling, this is the scale at which most empirical segregation indices are computed. In the case of Sugarscape, it corresponds to the whole city if the model is a metaphor for city resources (Batty, 2005), or to a generic landscape where a resource is grown otherwise. In both cases, our point is that there exist many different patterns of density distribution in resource location and urban density, and that not acknowledging this diversity leads to potentially false results. Furthermore, in urban models, we argue that the hypothesis of isotropic density is potentially the most common simplification of the heterogeneity of space, with consequences on the model outputs often not evaluated.

@@

	% 9. The authors should illustrate the contribution of each parameter of the generator to the generated initial pattern using a figure. Details of the generators should be included in an appendix
	\item The behavior of the spatial generator was described with more details in Appendix.

	% 10. Explain how the density grids are used in the Schelling model, do you allow more than one agent to be in the same cell? 
	\item Regarding the use of the density grid in the Schelling model, yes we allow more agents to be in the same cell. The potential density is defined by the density grid generated, and its population with the same number of agents in all grids. This distribution is the one at initialisation. If the potential density is not reached, more agents can move in the cell, otherwise it is deemed full and unavailable for further moves. The satisfaction and segregation indices are computed with regard to the people in the cell and the people present in neighbouring cells.

	% 11. Line 297: I am not sure why empirical density destitutions of cities are important in the context of this study. 
	\item Density distributions of empirical cities are important because we want to test models with realistic ranges of initial patterns of density distribution. Therefore we cannot limit ourselves to a single 2-peak mountain in the classical Sugarscape model and an isotropic square city in Schelling. We chose to use actual distribution of European cities to constraint our density generation.

@@

	% Page 2 line 98: “However, this step is rarely explicit and authors tend to generalize the conclusion of the model from a single, spatial case study”. I do not understand the first part of the this statement. The steps taken are often very explicit. Due to the amount of time it takes to correctly represent all spatial data, including population densities and the variation of other population variables over space, many authors indeed restrict themselves to a single case study due to the time intensity of this task. Many agent-based models are also not valid for other areas.
	\item What we meant was actually that this step is rarely explicit and authors are therefore not able to generalize the conclusion of the simulations to other spatial context. We rephrased the paragraph accordingly.

	% The authors do not differentiate between data driven empirical models versus theory-driven models. I think a clear differentiation between the two groups and the positioning of the two case studies in the second group would make the paper more balanced.
	\item Concerning the remarks on synthetic population generation and the different types of models, we clearly stated our positioning regarding models built from theory, for which the proposed sensitivity analysis workflow is more suited and that our two case studies illustrate.

	% In section 1.3 (Previous considerations on the effects of the spatial configuration in simulation models) authors provide a lot of evidence on previous work on the impact of initial spatial conditions on the output of models. This is contrary to the statement in the abstract that initial conditions are often taken for granted.
	\item Indeed, we have tried to review articles where some kind of sensitivity to initial spatial conditions are tackled. However we would like to emphasize that the references cited in this section are few compared to the mass of geosimulation articles published with hardly any mention of dependence of output on initial spatial condition. Moreover, even if such sensitivity is analysed, it mostly provide some hints of impact of initial spatial conditions on the output of models (due to the accuracy of data, shape of boundaries and spatial heterogeneity) but to the best of our knowledge no article provide a systematic inquiry into the impact of systematically defined spatial input on the model output in the way we try to provide later on in the paper. We have tried to argue this point at the end of the first section.

@@

	% In places the English along with the overall argument could be better articulated. For example, on page 1 you write: “We think simulation can become a very good tool to achieve this,”  Could this be rewritten or better argued. You are not the only one to believe this but you don’t show this in your paper.
	\item We have worked towards improving the English along with the overall argument.

	% Page 4: you write “Generally, sensitivity analyses have focused either on the spatial context (extent of the environment, shape of the zones if applicable - squares, hexagons, etc., objects - links, rasters, etc.); either on the spatial encoding of the heterogeneity of space (algorithms of disaggregation, interpolation, etc.), but rarely on both at the same time” This makes little sense. What it should be is “Generally, sensitivity analyses have focused either on the spatial context or the heterogeneity of space” or something like that. Basically you need the “or”.
	\item Thank you for the suggestion on page 4. We have modified the paragraph accordingly.

	% You write “To our knowledge there exist no single well established method to compare phase diagrams in the agent-based modelling and geosimulation literature.” As this is new you may want to discuss how say its done in other fields?  
	\item We do not have knowledge of examples in which the comparison of patterns or fields is called ``phase diagram comparison'', and we neither have knowledge of such work in physics for example, from which the term originated. There is naturally all the literature we cited on similar issues in other domains, and the extension of the discussion gives elements of answer to this point.

	% In the Schelling and sugarscape models how are the initial population of agents distributed? Is it random? I ask as this is unclear in the current version of the paper but it is vital if your purpose is to explore how the initial spatial configuration impacts the results of the model. Should the agents not be all located at the same location for each run to rule out the impact of initial placement of agents on the resulting patterns? This is something that is not addressed in the paper. I know for example, the Schelling model in NetLogo normally places the agents at random locations but in your reimplementation how is this done? The same goes for the sugarscape model in NetLogo. I believe a clearer description of the model initialization would be good and how its not the initial random placement of agents but the actual environment that impacts the outcomes. Maybe this was explained in the paper but I missed it.  
	\item Regarding the way these models are used in the literature, yes, the initial distribution of agents is classically random in both models and, most importantly for our point, it follows a uniform distribution of density. In our implementation, the initial location of agents is also random in Schelling, but it follows a distribution of density given by the generated grid. In Sugarscape, the agents are initialised at random but the resources follow a distribution of density given by the generated grid. We have clarified this point in section 2.3.

@@

	% Also I appreciate you are trying to show rather complex results but reading the results several times I found the presentation of them (both written and visual) really hard to follow and understand. I was wondering if maybe you could find a better way to show / discuss them. Maybe a  worked example of how each set of parameters leads to a point in say Figure 4. Also it is confusing why the results from both models are not presented using the same styles of figures. For example, for the sugar scape model you different styles of figures than for the segregation model.
	\item Additional figures for the Schelling model presenting the results in a similar way were provided and commented in a way that tries to make it easier to grasp for the reader. Unfortunately, the figures showing grid estimates of phase diagrams could not be realized for the Schelling model because of the different sampling of the parameter space used.

\end{itemize}

Concerning the comments made by the fourth referee:

\begin{itemize}
	% In sensitivity analysis of spatial models, stochastic effects and small parameter changes are normally applied. What about initial conditions? The authors test the effects of different arrangements (e.g. monocentric vs. polycentric density patterns) on agent-based Schelling segregation models and Sugarscape's unequal societies model. Overall, I find this to be a very good paper. Very well written in general. Good review of the problem, clearly outlining (with references) the need for focus on initial conditions in geosimulation. The chief factors (data uncertainty, nature of spatial units (e.g. shape) and spatial heterogeneity) on initial spatial conditions are covered: -how many of these do you test? I see heterogeneity addressed, but what about shape and uncertainty? You touch upon shape when talking about NetLogo's use of raster as opposed to vector in the Discussion - could you expand on this?
	\item We thank the reviewer for this good remark regarding connected issues such as heterogeneity or the choice raster/vector. We provide references to papers addressing these issues. However, we have not addressed the shape of cells and the uncertainty of data in this paper, only the diversity of shapes of urban morphologies (e.g. heterogeneity).

### 2018-09-28 paper.tex
final

%\usepackage[final]{changes}
\usepackage{changes}

@@

\address[a]{UPS CNRS 3611 ISC-PIF, Paris, France}
\address[b]{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France}
\address[c]{Centre for Advanced Spatial Analysis, University College London, UK}
\address[d]{UMR CNRS 8097 Centre Maurice Halbwachs, Paris, France}
\address[e]{UMR 6266 IDEES, Universit{\'e} de Rouen Normandie, France}
\address[f]{Universit{\'e} Paris-Est, Laboratoire Ville Mobilité Transport, Marne-la-Vallée, France}

@@

\added{As detailed in supplementary material~\ref{app:convergence}, more repetitions are needed for Schelling indicators than for Sugarscape, in order to obtain a similar relative confidence in the estimation of averages. We ran for this reason a different number of replications for each model.}

@@

We measure the distance of the phase diagrams for all density grids with respect to the reference phase diagram computed on the default initial spatial condition setup (a bi-centric symmetrical non toroidal configuration) using the measure defined in equation~\ref{eq:phase-distance}. For each density grid, we obtain the average squared distance between corresponding points of the phase diagrams, i.e. the \replaced{mean}{median} value of the final output measure, such as segregation or inequality, for a given value of parameters in the two setups (isotropic and generated). This average squared distance for each point is then related to the average variance of each of the phase diagram (the reference one and the one for the grid under inquiry). Therefore, values greater than 1 will mean that inter-diagram variability is more important than intra-diagram variability. \added{We tested the sensitivity to the type of distance, using a Minkovski distance with a varying exponent. The results are presented in supplementary material~\ref{app:distances}, and show a similar sensitivity to spatial initial conditions.}

@@

%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{figures/relativedistance_metaparams}
\caption{\textbf{Relative distances of phase diagrams by initial spatial grids described by \replaced{their generator parameters}{the meta-parameters of their generator}.} Relative distance as a function of \replaced{generator parameters}{meta-parameters} $\alpha$ (strength of preferential attachment) and $\beta$ (strength of diffusion process).}
\label{fig:sugarscape-distance-meta}
\end{figure*}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{figures/relativedistance_morphspace}
\caption{\textbf{Relative distances of phase diagrams to the reference across grids.} Relative distance as a function of two first principal components of the morphological space (see text). Black point correspond to the reference spatial configuration. Green frame and blue frame give respectively the first and second particular phase diagrams shown in Fig.~\ref{fig:sugarscape-phasediagrams}.}
\label{fig:sugarscape-distance-pca}
\end{figure*}
%%%%%%%%%%%%%

@@

Another way to go would be to implement additional generators, such as social networks \citep{alizadeh2016generating} with localised agents, \added{transportation networks generators \citep{raimbault2018multi}, or coupled road network and population raster generators \citep{raimbault2018urban}.}

@@

\added{We give in Fig.~\ref{fig:stylized-generator} plots roughly summarizing the behavior of the density grid generator, according to parameters $(\alpha,\beta)$. To put it in a simple way, high values of $\alpha$ give highly hierarchical configurations, and diminishing $\beta$ increase the number of centers. Low values of $\alpha$ give diffuse patterns, with however clear centers for a high diffusion. We do not discuss it the role of other parameters, but according to \cite{raimbault2018calibration}, diffusion steps give smoother forms, and the rate between total population and the population increment at each step (which is equivalent to the total number of steps) is crucial to select non-stationary distributions that are closer to real configurations. \cite{raimbault2018calibration} also shows the existence of non-linear behaviors in some regions of the parameter space, so the description we gave here shall not be interpreted as a linear link between generator parameters and the morphological properties of the generated grids.}

@@

\added{For both models we estimate the Sharpe ratios for each indicator by $S(X) = \hat{\mathbb{E}{X}}/\hat{\sigma}(X)$ with standard estimators for average and standard deviation. The summary statistics of this ratio computed on repetitions for all parameter points are given in Table~\ref{tab:summarysharpes}. Under the assumption of a normal distribution, the width of the confidence interval at level $c$ is given by $\left|\mu_+ - \mu_-\right| = 4\cdot\sigma \sigma z_{c} \sqrt{n}$ where $\sigma$ is the standard deviation, $z_{c}$ is the quantile at which $c$ is attained by the cumulative distribution, which is around $1.96$ for a 95\% confidence interval. This means that to obtain a confidence interval of width $\kappa \cdot \sigma$, one needs a number $n \simeq (8 / \kappa )^2$ of repetitions. This gives 64 repetitions for $\kappa = 1$. As the Sharpes ratios are in general smaller for Schelling indicators than for Sugarscape, we take $n = 50$ for Sugarscape and $n = 100$ for Schelling to have s similar confidence in estimations.}

@@

\added{We describe here the tests done with other distances to compare phase diagrams. We tested normalized Minkovski distances, defined by $d(x,y) = \left(\frac{1}{N}\cdot \sum_i \left|x_i - y_i\right|^{q}\right)^{\frac{1}{q}}$, for varying values of $q$ from $q = 1$ (Manhattan distance) to $q = 10$, including $q = 2$ (Euclidian distance) which is used in main text. The Table~\ref{tab:schellingdistances} gives the summary statistics of each distance computed on all initial configurations for the Schelling model. The Table~\ref{tab:sugarscapedistances} gives the same statistics for the sugarscape model. We naturally obtain smaller difference with the Manhattan distance but which remain significant (averages of 10\% for the Schelling model and 40 \% for Sugarscape), and variabilities with higher values of the Minkovski exponent are much higher. This results confirm the high variability observed in main text with the Euclidian distance.}

@@

\added{We give below the pseudo-code for the implementations we used of both sugarscape and schelling models. We recall that source code is openly available at} \url{https://github.com/AnonymousAuthor2/SpaceMatters}. \added{The pseudo-code is in the style of NetLogo code, which is already easily readable.}

%%%%%%%%%%%%%%%
\begin{figure*}
\caption{\added{\textbf{Pseudo-code (NetLogo style) for the Schelling model used here.} We give a pseudo-code very close to the NetLogo language, at the exception of italic expressions which are not put here in NetLogo to ease understandability.}}
\bigskip
\begin{mdframed}
\begin{lstlisting}
while (*@\textit{not stopping-condition}@*) [
	ask turtles [
		set unsatisfied? false
		let neighboragents turtles in-radius neighborhood-radius
		let wantedcolor color
		let stranger-rate count neighboragents with [color = wantedcolor] /
			count neighboragents
		if stranger-rate < similar-wanted [
			set unsatisfied? true random-move
		]
	]
    \end{lstlisting}
    \end{mdframed}
\end{figure*}
%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%
\begin{figure*}
% Minimal netlogo code for the sugarscape model
\caption{\added{\textbf{Pseudo-code (NetLogo style) for the sugarscape model.} Conventions are the same than for Schelling pseudo-code.}}
\bigskip
\begin{mdframed}
\begin{lstlisting}
while [time < final-time] [
	;regrow the patch resources
    ask patches [set psugar min (list max-psugar (psugar + 1))]

>>>>

\usepackage[final]{changes}
%\usepackage{changes}

@@

\address[a]{UPS CNRS 3611 ISC-PIF, Paris, France}
\address[b]{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France}
\address[c]{Centre for Advanced Spatial Analysis, University College London, UK}
\address[d]{UMR CNRS 8097 Centre Maurice Halbwachs, Paris, France}
\address[e]{UMR 6266 IDEES, Universit{\'e} de Rouen Normandie, France}
\address[f]{Universit{\'e} Paris-Est, Laboratoire Ville Mobilit{\'e} Transport, Marne-la-Vallée, France}

@@

\added{As detailed in~\ref{app:convergence}, more repetitions are needed for Schelling indicators than for Sugarscape, in order to obtain a similar relative confidence in the estimation of averages. We ran for this reason a different number of replications for each model.}

@@

We measure the distance of the phase diagrams for all density grids with respect to the reference phase diagram computed on the default initial spatial condition setup (a bi-centric symmetrical non toroidal configuration) using the measure defined in equation~\ref{eq:phase-distance}. For each density grid, we obtain the average squared distance between corresponding points of the phase diagrams, i.e. the \replaced{mean}{median} value of the final output measure, such as segregation or inequality, for a given value of parameters in the two setups (isotropic and generated). This average squared distance for each point is then related to the average variance of each of the phase diagram (the reference one and the one for the grid under inquiry). Therefore, values greater than 1 will mean that inter-diagram variability is more important than intra-diagram variability. \added{We tested the sensitivity to the type of distance, using a Minkovski distance with a varying exponent. The results are presented in~\ref{app:distances}, and show a similar sensitivity to spatial initial conditions.}

@@

%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{figures/relativedistance_metaparams.png}
\caption{\textbf{Relative distances of phase diagrams by initial spatial grids described by \replaced{their generator parameters}{the meta-parameters of their generator}.} Relative distance as a function of \replaced{generator parameters}{meta-parameters} $\alpha$ (strength of preferential attachment) and $\beta$ (strength of diffusion process).}
\label{fig:sugarscape-distance-meta}
\end{figure*}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{figures/relativedistance_morphspace.png}
\caption{\textbf{Relative distances of phase diagrams to the reference across grids.} Relative distance as a function of two first principal components of the morphological space (see text). Black point correspond to the reference spatial configuration. Green frame and blue frame give respectively the first and second particular phase diagrams shown in Fig.~\ref{fig:sugarscape-phasediagrams}.}
\label{fig:sugarscape-distance-pca}
\end{figure*}
%%%%%%%%%%%%%

@@

Another way to go would be to implement additional generators, such as social networks \citep{alizadeh2016generating} with localised agents, \added{transportation networks generators \citep{raimbault2018multi}, or coupled road network and population raster generators \citep{raimbault2018urban}.}
% Generators of abstract urban systems at a macroscopic scale could also be useful tools to better understand urban growth models as sketched by \cite{raimbault2018unveiling}.}

@@

\added{We give in Fig.~\ref{fig:stylized-generator} plots roughly summarizing the behavior of the density grid generator, according to parameters $(\alpha,\beta)$. To put it in a simple way, high values of $\alpha$ give highly hierarchical configurations, and diminishing $\beta$ increase the number of centers. Low values of $\alpha$ give diffuse patterns, with however clear centers for a high diffusion. We do not discuss here the role of other parameters, but according to \cite{raimbault2018calibration}, diffusion steps give smoother forms, and the rate between total population and the population increment at each step (which is equivalent to the total number of steps) is crucial to select non-stationary distributions that are closer to real configurations. \cite{raimbault2018calibration} also shows the existence of non-linear behaviors in some regions of the parameter space, so the description we gave here shall not be interpreted as a linear link between generator parameters and the morphological properties of the generated grids.}

@@

\added{For both models we estimate the Sharpe ratios for each indicator by $S(X) = \hat{\mathbb{E}}\left[X\right]/\hat{\sigma}(X)$ with standard estimators for average and standard deviation. The summary statistics of this ratio computed on repetitions for all parameter points are given in Table~\ref{tab:summarysharpes}. Under the assumption of a normal distribution, the width of the confidence interval at level $c$ is given by $\left|\mu_+ - \mu_-\right| = 4\cdot \sigma \cdot z_{c} / \sqrt{n}$ where $\sigma$ is the standard deviation, $z_{c}$ is the quantile at which $c$ is attained by the cumulative distribution, which is around $1.96$ for a 95\% confidence interval. This means that to obtain a confidence interval of width $\kappa \cdot \sigma$, one needs a number $n \simeq (8 / \kappa )^2$ of repetitions. This gives 64 repetitions for $\kappa = 1$. As the Sharpe ratios are in general smaller for Schelling indicators than for Sugarscape, we take $n = 50$ for Sugarscape and $n = 100$ for Schelling to have a similar confidence in estimations.}

@@

\added{We describe here the tests done with other distances to compare phase diagrams. We tested normalized Minkovski distances, defined by $d(x,y) = \left(\frac{1}{N}\cdot \sum_i \left|x_i - y_i\right|^{q}\right)^{\frac{1}{q}}$, for varying values of $q$ from $q = 1$ (Manhattan distance) to $q = 10$, including $q = 2$ (Euclidian distance) which is used in main text. The Table~\ref{tab:schellingdistances} gives the summary statistics of each distance computed on all initial configurations for the Schelling model. The Table~\ref{tab:sugarscapedistances} gives the same statistics for the sugarscape model. We naturally obtain smaller difference with the Manhattan distance but which remain significant (averages of 10\% for the Schelling model and 40 \% for sugarscape), and variabilities with higher values of the Minkovski exponent are much higher. This results confirm the high variability observed in main text with the Euclidian distance.}

@@

\added{We give below the pseudo-code for the implementations we used of both sugarscape (Fig.~\ref{frame:sugarscapecode}) and Schelling (Fig.~\ref{frame:schellingcode}) models. We recall that source code is openly available at} \url{https://github.com/AnonymousAuthor2/SpaceMatters}. \added{The pseudo-code is in the style of NetLogo code, which is already easily readable.}

%%%%%%%%%%%%%%%
\begin{figure*}
\caption{\added{\textbf{Pseudo-code (NetLogo style) for the Schelling model used here.} We give a pseudo-code very close to the NetLogo language, at the exception of italic expressions which are not put here in NetLogo to ease understandability.}}\label{frame:schellingcode}
\bigskip
\begin{mdframed}
\begin{lstlisting}
while (*@\textit{not stopping-condition}@*) [
	ask turtles [
		set unsatisfied? false
		let neighboragents turtles in-radius neighborhood-radius
		let wantedcolor color
		let stranger-rate count neighboragents with [color = wantedcolor] /
			count neighboragents
		if stranger-rate < similar-wanted [
			set unsatisfied? true random-move
		]
	]
    \end{lstlisting}
    \end{mdframed}
\end{figure*}
%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%
\begin{figure*}
% Minimal netlogo code for the sugarscape model
\caption{\added{\textbf{Pseudo-code (NetLogo style) for the sugarscape model.} Conventions are the same than for Schelling pseudo-code.}}\label{frame:sugarscapecode}
\bigskip
\begin{mdframed}
\begin{lstlisting}
while [time < final-time] [
    ;regrow the patch resources
    ask patches [set psugar min (list max-psugar (psugar + 1))]
